The Distributional Impacts of the Electricity Transition on Pollution Exposure

### 2024-12-05 MIP_Downscaled.tex

\author{Lauren Beatty\thanks{Environmental Defense Fund  \hspace{.5cm} E-mail: lbeatty1@edf.org \hspace{.5cm}Website: \href{https://lbeatty1.github.io}{https://lbeatty1.github.io}}, 
Matthias Fripp\thanks{Environmental Defense Fund}, 
Greg Schivley, 
Rangrang Zhang, 
Cameron Wade, 
Oleg Lugovoy, 
Michael Roberts, 
Patricia Hildalgo}

>>>>

\author{Lauren Beatty\thanks{Environmental Defense Fund  \hspace{.5cm} E-mail: lbeatty1@edf.org \hspace{.5cm}Website: \href{https://lbeatty1.github.io}{https://lbeatty1.github.io}}, 
Matthias Fripp, 
Greg Schivley, 
Rangrang Zhang, 
Cameron Wade, \\ 
Oleg Lugovoy, 
Michael Roberts, 
Patricia Hildalgo}
